Index-aware learning of circuits

### 2024-02-26 doc/article/arxiv/article.tex
alternative definition of G

In order to obtain a version of \eqref{eq:md_mnai} that is better suited to analysis and implementation, we consider the device function Jacobians
\begin{align}
    \mb{G} \big( \AT{R} \vphi \big) \coloneqq \mb{J}_{\AT{R} \vphi}(\gR), \quad \mb{L}(\i{L}) \coloneqq \mb{J}_{\i{L}}(\phiL), \quad \mb{C} \big( \AT{C} \vphi \big) \coloneqq \mb{J}_{\AT{C} \vphi}(\qC), \label{eq:md_dfj}
\end{align}
where we use the same notation for the Jacobians as in \autoref{sec:int}. Inserting \eqref{eq:md_dfj} into the original system, while linearizing $\gR$ and writing everything in matrix form, yields
\begin{align}
    \begin{bmatrix}
        \A{C}^{\phantom{\T}} \mb{C} \big( \AT{C} \vphi \big) \AT{C} & &\\
        & \mb{L}(\i{L}) &\\
        & & \mb{0}
    \end{bmatrix} \ddt \begin{bmatrix}
        \vphi\\
        \i{L}\\
        \i{V}
    \end{bmatrix} + \begin{bmatrix}
        \A{R}^{\phantom{\T}} \mb{G} \big( \AT{R} \vphi \big) \AT{R} & \A{L} & \A{V}\\
        -\AT{L} & &\\
        -\AT{V} & &
    \end{bmatrix} \begin{bmatrix}
        \vphi\\
        \i{L}\\
        \i{V}
    \end{bmatrix} + \begin{bmatrix}
        \A{I} \i{s}(t)\\
        \mb{0}\\
        \v{s}(t)
    \end{bmatrix} = \mb{0}, \label{eq:md_mnaii}
\end{align}
assuming that $\phiL$ and $\qC$ do not explicitly depend on time.

>>>>

\textcolor{red}{In order to obtain a version of \eqref{eq:md_mnai} that is better suited to analysis and implementation, we consider the device function Jacobians\footnote{\textcolor{red}{Note that, for nonzero denominators, $\mb{G}$ may also be defined componentwise as
\begin{align*}
    \big[ \mb{G} \big( \AT{R} \vphi \big) \big]_{ij} = \frac{\big[ \gR(\AT{R} \vphi) \big]_i}{\big[ \AT{R} \vphi \big]_j},
\end{align*}
such that \eqref{eq:md_mnai} and \eqref{eq:md_mnaii} become truly equivalent. (The components with zero denominators are set to zero.) This alternative definition has no impact on our approach, however practical implementations often work with $\mb{G}$ as defined in \eqref{eq:md_dfj}.}}}
\begin{align}
    \mb{G} \big( \AT{R} \vphi \big) \coloneqq \mb{J}_{\AT{R} \vphi}(\gR), \quad \mb{L}(\i{L}) \coloneqq \mb{J}_{\i{L}}(\phiL), \quad \mb{C} \big( \AT{C} \vphi \big) \coloneqq \mb{J}_{\AT{C} \vphi}(\qC), \label{eq:md_dfj}
\end{align}
where we use the same notation for the Jacobians as in \autoref{sec:int}. Inserting \eqref{eq:md_dfj} into the original system and writing everything in matrix form yields
\begin{align}
    \begin{bmatrix}
        \A{C}^{\phantom{\T}} \mb{C} \big( \AT{C} \vphi \big) \AT{C} & &\\
        & \mb{L}(\i{L}) &\\
        & & \mb{0}
    \end{bmatrix} \ddt \begin{bmatrix}
        \vphi\\
        \i{L}\\
        \i{V}
    \end{bmatrix} + \begin{bmatrix}
        \A{R}^{\phantom{\T}} \mb{G} \big( \AT{R} \vphi \big) \AT{R} & \A{L} & \A{V}\\
        -\AT{L} & &\\
        -\AT{V} & &
    \end{bmatrix} \begin{bmatrix}
        \vphi\\
        \i{L}\\
        \i{V}
    \end{bmatrix} + \begin{bmatrix}
        \A{I} \i{s}(t)\\
        \mb{0}\\
        \v{s}(t)
    \end{bmatrix} = \mb{0}, \label{eq:md_mnaii}
\end{align}
assuming that $\phiL$ and $\qC$ do not explicitly depend on time.
